### 2014-02-23 paper/retrofit.tex
Proof of TSNI theorem (relying on a not-yet-existing lemma with the main proof).

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \[
    |its1| \approx_{|il|} |its2| \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \]
  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
  \[
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'| \qquad \text{and} \qquad
    |its1'| \approx_{|il|} |its2'|
    \ \text{.}
  \]
\end{theorem}

>>>>

\begin{theorem}[Termination Sensitive Non-Interference (TSNI)]
  For any two list of tasks |its1|, |its2|, |its2|, label |il|,
  IFC states |iS1|, |iS2|, |iS1'|, where
  \begin{equation} \label{eq:tsni-lhs}
    |its1| \approx_{|il|} |its2|
    \qquad \text{and} \qquad
    |iconf iS1 its1| |.->|^* |iconf iS1' its1'|
  \end{equation}
  then there exists a list of tasks |ts2'| and an IFC state |iS2'| such that
  \begin{equation} \label{eq:tsni-rhs}
    |its1'| \approx_{|il|} |its2'|
     \qquad \text{and} \qquad
    |iconf iS2 its2| |.->|^* |iconf iS2' its2'|
    \ \text{.}
  \end{equation}
\end{theorem}

\begin{proof}
  We proof the theorem by induction on the length of the derivation sequence in~(1).
  The base case for derivations
  of length 0 is trivial, allowing
  us to simple chose $|its2'=its2|$ and $|iS2'=iS2|$.  In the step case, we assume
  the theorem holds for derivation sequences of length up to $n$, and show that it also
  holds for those of length $n+1$.  We split the derivation sequence from~(1) as follows:
  \[
  |iconf iS1 its1| |.->| |iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|
  \]
  for some IFC state |iS1''| and task list |its1''|.  By Lemma~1, we get
  |its2''| and |iS2''| with
  \begin{equation} \label{eq:tsni-proof-1}
  |its1''| \approx_{|il|} |its2''|
  \qquad \text{and} \qquad
  |iconf iS2 its2| |.->|^* |iconf iS2'' its2''|
  \end{equation}
  Applying the induction hypotisis to
  $|iconf iS1'' its1''| |.->|^n |iconf iS1' its1'|$, we get |its2'| and |iS2'| with
  \begin{equation} \label{eq:tsni-proof-2}
  |its1'| \approx_{|il|} |its2'|
  \qquad \text{and} \qquad
  |iconf iS2'' its2''| |.->|^* |iconf iS2' its2'|
  \end{equation}
  Stitching together the derivation sequences from (3) and (4) directly gives
  us (2), which concludes the proof.
\end{proof}
